---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BRVM

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/BRVM)](https://cran.r-project.org/package=BRVM)
![](https://cranlogs.r-pkg.org/badges/BRVM)
![](https://cranlogs.r-pkg.org/badges/grand-total/BRVM)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html##experimental)
[![PRs Welcome](https://img.shields.io/badge/PRs-welcome-brightgreen.svg?style=flat-square)](https://makeapullrequest.com)
<!-- badges: end -->

# BRVM
BRVM is an R package that provides real-time data from the BRVM ("Regional Securities Exchange SA" call Bourse Régionale des Valeurs Mobilières in french).  As a goal, we want to facilitate access to data for all users of the R programming language. This package includes a variety of data accessible just by function call.

BRVM est un package R qui permet d’obtenir des données à temps réel de la BRVM (Bourse Régionale des Valeurs Mobilières). Comme objectif, nous voulons faciliter l’accès aux données à tous les utilisateurs du langage de programmation R. Ce package comporte une diversité de données accessibles juste par appel de fonction.


## Installation

You can install the development version of BRVM from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Koffi-Fredysessie/BRVM")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BRVM)
```

Lets take a look at a simple function that will get any n number of records based
on whether they are 'Top' or 'Bottom' ranked.

```{r brvm_rank}
BRVM_rank("Top", 10)
```

